### 2023-01-14 paper-reviews/papers-2023.tex
Improve ispc description

\section*{Compilers}
\begin{itemize}
    \item The paper presents ispc --- Intel SPMD Program Compiler. The paper introduces new SPMD-on-SIMD concept that seems to be quite reasonable for running effectively compiling SPMD programs for CPUs. A few specific optimizations are introduced to enable efficient usage of a CPU's SIMD hardware unit. The project looks like an interesting alternative to hand-written intrinsic-based optimizations. The project is still alive at the moment of writing the note. I can also see a few well familiar names in the list of contributors. As a side note, the paper can be a good reference for \href{https://github.com/yulyugin/mipt-parallel-computing}{<<MIPT parallel computing>> course} if that one ever gets back to live:

>>>>

\section*{Compilers}
\begin{itemize}
    \item The paper presents ispc --- Intel SPMD Program Compiler. A new <<SPMD-on-SIMD>> concept is introduced. The concept seems to be quite reasonable for efficient compilation of SPMD programs for CPUs. A few specific optimizations are described to enable better usage of a CPU's SIMD hardware unit. The project looks like an interesting alternative to hand-written intrinsic-based optimizations. The project is still alive at the moment of writing the note. I can also see a few well familiar names in the list of contributors. As a side note for myself, the paper can be a good reference for \href{https://github.com/yulyugin/mipt-parallel-computing}{<<MIPT parallel computing>> course} if that one ever gets back to live:
